About {\bf llvm2aa}

### 2011-08-25 v2/llvmbc2Aa/docs/llvm2aa.tex
updated

The options:
\begin{itemize}
\item {\bf -modules=listfile} : Specify the list of functions in the bytecode
which should be converted to \Aa.   The names of these functions should be
listed in the text-file listfile. If this option is not specified, all functions
are converted.
\item {\bf -storageinit} :  Storage objects in the llvm bytecode
are explicitly initialized in the generated \Aa code.   An initializer
routine {\bf global\_storage\_initializer\_} is instantiated in
the \Aa code for this purpose.
\item {\bf llvmpasses} : {\bf llvm2aa} uses the LLVM compiler
infrastructure to perform LLVM byte-code optimizations.  A large list
of these optimizations is available through the llvm2aa command-line.
For more details, see LLVM documentation at http://www.llvm.org.
\end{itemize}

@@

Several LLVM byte-code constructs are not supported.  Most 
importantly:
\begin{itemize}
\item Function pointers are not supported.
\item Functions with a variable number of arguments are not 
supported.
\item Calls to LLVM intrinsics are just passed through to the
output \Aa file.  The \Aa file will then contain calls
to these intrinsics without there being a corresponding
module declaration in the \Aa file.
\item If the LLVM byte-code has cycles in its call graph,
then the code is translated, but will create an error
in downstream \Aa analysis and transformation tools.
\item System calls made from the \Aa code are simply
passed through and would need to be supplied as an
\Aa library in order to perform downstream analysis and
transformation.
\item The LLVM integer, floating-point, array, structure,
vector and void types are the only ones currently supported.
\item The LLVM switch instruction is currently not supported,
but support is planned in the near future.
\item The LLVM indirect-branch, invoke, unwind and unreachable
instructions will not be supported.
\item The LLVM division and remainder instructions are currently
not supported.  Support for these is planned.
\item LLVM vector instructions are currently not supported.
\item LLVM aggregate instructions (extractvalue, insertvalue)
are currently not supported, but will be supported in the
near future.
\end{itemize}

>>>>

The options:
\begin{itemize}
\item {\bf -modules=listfile} : Specify the list of functions in the bytecode
which should be converted to \Aa.   The names of these functions should be
listed in the text-file listfile. If this option is not specified, all functions
are converted.
\item {\bf -storageinit} :  Storage objects in the llvm bytecode
are explicitly initialized in the generated \Aa code.   An initializer
routine {\bf global\_storage\_initializer\_} is instantiated in
the \Aa code for this purpose.
\item {\bf llvm2aa} uses the LLVM compiler
infrastructure to perform LLVM byte-code optimizations.  A large list
of these optimizations is available through the llvm2aa command-line.
For more details, see LLVM documentation at http://www.llvm.org.
\end{itemize}

@@

Several LLVM byte-code constructs are not supported.  Most 
importantly:
\begin{itemize}
\item Function pointers are not supported.
\item Functions with a variable number of arguments are not 
supported.
\item Calls to LLVM intrinsics are just passed through to the
output \Aa file.  The \Aa file will then contain calls
to these intrinsics without there being a corresponding
module declaration in the \Aa file.
\item If the LLVM byte-code has cycles in its call graph,
then the code is translated, but will create an error
in downstream \Aa analysis and transformation tools.
\item System calls made from the \Aa code are simply
passed through and would need to be supplied as an
\Aa library in order to perform downstream analysis and
transformation.
\item The LLVM integer, floating-point, array, structure,
vector and void types are the only ones currently supported.
\item The LLVM indirect-branch, invoke, unwind and unreachable
instructions will not be supported.
\item The LLVM division and remainder instructions are currently
not supported. 
\item LLVM vector instructions are currently not supported.
\item LLVM aggregate instructions (extractvalue, insertvalue)
are currently not supported, but will be supported in the
near future.
\end{itemize}
